Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-14 manuscript/manuscript.Rmd
no more 3D stable points, added r_X(t) part

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 8 or 9 for wide ranges of parameter values.
Fig. \ref{fig:fixed points} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stX.png}
    \caption{$X$ component of fixed points.}
    \label{fig:stx}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stY.png}
    \caption{$Y$ component of fixed points.}
    \label{fig:sty}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.32\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/stZ.png}
    \caption{$Z$ component of fixed points.}
    \label{fig:stz}
  \end{subfigure}
  \caption{Numerically-computed fixed points of the three-species deterministic model, eq. \eqref{eq:3d model}.
  Here, the parameter $D$ was varied between 0.75 and 1.25, and the values of the other parameters are fixed as in eq. \eqref{eq:param vals}. 
  The three components of the fixed points are plotted separately, as a function of $D$.}
  \label{fig:fixed points}
\end{figure}

Throughout most of this paper we will fix the parameters of the model according to eq. \eqref{eq:param vals}.
At these values, the fixed points of the model are:\footnote{
We have included only three decimal digits for readability.
These fixed points may be generated by running the ‘‘stable\_points.py’’ script in \url{https://github.com/boettiger-lab/approx-model-or-approx-soln}.
}
\begin{align*}
  (X,Y,Z) \approx 
  &(0.839, 0.054, 0.377), \quad 
    (0.048, 0.774, 0.480), \quad
    (0.359, 0.491, 0.509), \\
    &(0.899, 0.000, 0.303), \quad
    (0.000, 0.818, 0.457), \quad
    (0.666, 0.666, 0.000), \\
    &(1.000,0.000,0.000),\quad (0.000,1.000,0.000),\quad (0.000,0.000,0.000).
\end{align*}
The classification of fixed points for multi-dimensional systems is generally more complicated than in one dimension.
A fixed point might be stable against perturbations in one direction, but unstable against perturbations along another.
While a detailed classification of these fixed points is beyond the scope of this work, we point out that the point $(0.839, 0.054, 0.377)$ is stable against perturbations in all directions.
We will thus use it as a starting point for our simulations.

>>>>

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
Here, a fixed point analysis provides a less intuitive picture of the dynamics---it no longer necessarily alternates in a tipping manner between two stable points.

For most of our paper, parameters used in this model will be given as in eq. \eqref{eq:param vals}.
In this paper we do not set out to provide a realistic model of any given fishery, but rather to show that the DRL approach may be applicable to a broad variety of plausible fish recruitment models.
Because of this, we also provide a *stability analysis*, where we perturb the parameter values randomly.
Finally, in the time-varying model, we use the following drift on the growth rate of $X$:
\begin{equation*}
  r_X = r_X(t) = \max(1-t/200, 1/2).
\end{equation*}
